---
title: "AssignmentB"
author: "Martijn Koster, William Schaafsma, Martijn van Dam, Victor Hovius"
date: "3/21/2022"
output: pdf_document
---



<style type="text/css">

body{ /* Normal  */
      font-size: 12px;
  }
td {  /* Table  */
  font-size: 12px;
}
h1.title {
  font-size: 28px;
  }
h1 { /* Header 1 */
  font-size: 22px;
  }
h2 { /* Header 2 */
    font-size: 18px;
  }
h3 { /* Header 3 */
  font-size: 14px;
  font-family: "Times New Roman", Times, serif;
  }
code.r{ /* Code block */
    font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 14px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, comment = NA, warning = FALSE,
                      error=FALSE, results='hide',fig.keep='all')
```

---

```{r, include=FALSE}
library(mice)
library(naniar)
library(ggplot2)
library(ggpubr)
library(tidySEM)
library(dplyr)
library(VIM)
library(knitr)
library(kableExtra)
``` 

```{r}
data0 <- readRDS("incomplete_data_g1.rds")
```

- verhaaltje over wat we gaan doen
- daadwerkelijk naive imputatie doen
- imputatie beschrijven (de plots o.a.)
- data invullen n.a.v. imputatie
- data beschrijven
- aangeven wat we willen veranderen voor assignment C

# Imputations{#Imp}

After observing the data for missing values, we now try to solve the missingness problem by doing multiple imputation with the package `mice`. In first instance we will use the default settings to impute the missingness, this will be further elaborated in the [Default Imputations](#defImp) section. After the the default imputations we will evaluate the quality of the imputations by examining multiple plots about the convergence and the distribution. This will be done in the [Evaluating Default Imputations](#evalImp) section. After evaluating the default imputations, we will make an outline of how the imputations can be improved, by using more sophisticated imputations. This will be discussed in the [Improving the Imputations](#improveImp) section.    


## Default Imputations{#defImp}
```{r}
pred <- mice(data0)$predictorMatrix
meth <- mice(data0)$method
m <- mice(data0)$m
maxit <- mice(data0)$maxit
```

```{r}
methW <- meth["weight"]
methH <- meth["height"]
methB <- meth["bmi"]
methA <- meth["active"]
methS <- meth["smoke"]
```

As mentioned before we will first use the default settings of `mice` to impute the missingness. In this section we will describe these settings.  



```{r predImp, results='hold'}
kbl(pred, caption = "Predictor Matrix of Default Imputations") %>% 
  kable_classic(full_width = FALSE, html_font = "Cambria" )
```

## Evaluating Default Imputations{#evalImp}


## Improving the Imputations{#improveImp}



```{r}
pred <- mice(data0, maxit = 0)$predictorMatrix

meth <- mice(data0, maxit = 0)$method

meth["weight"] <- "~ I(bmi * (height / 100)^2)"

pred[c("height", "bmi"), "weight"] <- 0
```

```{r}
imp <- mice(data0, 
            m = 5, 
            maxit =  15,
            predictorMatrix = pred,
            method = meth,
            seed = 26011994,
            print = FALSE)
plot(imp)
densityplot(imp)
stripplot(imp)
```

