---
title: "Assingment A: Investigating the scope of the missingness problem"
author: "William Schaafsma"
date: "24-2-2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

The matter of interest for this assignment will be the impact that incomplete data (**observed data**) have on our inferences compared to the inferences we make with complete data (**true data**). To investigate the effect that missing values have on model inferences, we will build a multiple regression model. 

Firstly, we provide descriptive statistics and correlations. In table \@ref(tab:obsData) we compare the head of the observed data and the true data. Additionally, in \@ref(tab:des) the means and variances are compared. With regard to correlations, we present two correlations matrices; one for the observed data \@ref(tab:corObs) and the other for the true data \@ref(tab:corTrue). 

Secondly, we present our multiple regression model in table \@ref(tab:reg). Our model consists of the outcome variable: *active heart rate* and the predictors: *age* and *smoke*. We also included an interaction effect between *bmi* and *sex*. The first three columns reflect the observed data, whereas the latter reflect the true data.

The research question we try to answer in accordance with our model is: *What influence does a person's age, smoking habits, sex and bmi have on their heart rate during excercise?*

Thirdly, we start by inspecting the missing values. Then, we try to find out where the missing values occur. In \@ref(fig:misspat) we begin by giving a global overview of the missingness. Then, in \@ref(fig:mnar-plot) we compare the distributions for the observed data and the missing values. 

Lastly, we perform t-tests on the variables containing missing values to check the type of missingness, either MNAR, MAR, or MCAR. We also provide plots here to visualize where the missing values occur.


```{r, include=FALSE}
library(mice)
library(naniar)
library(ggplot2)
library(ggpubr)
library(tidySEM)
library(dplyr)
library(VIM)
library(knitr)
library(kableExtra)
``` 


## Default Imputations{#defImp}
```{r}
pred <- mice(data0)$predictorMatrix
meth <- mice(data0)$method
m <- mice(data0)$m
max <- mice(data0)$maxit
```




```{r}
data0 <- readRDS("incomplete_data_g1.rds")
```

```{r}
summary(data0)
```

```{r}
pred <- mice(data0, maxit = 0)$predictorMatrix
pred
```


```{r}
methW <- meth["weight"]
methH <- meth["height"]
methB <- meth["bmi"]
methA <- meth["active"]
methS <- meth["smoke"]
```

```{r}
meth
```

As mentioned before we will first use the default settings of `mice` to impute the missingness. In this section we will describe them. By default, `mice` will produce `r m` imputations and 5 iterations `r maxit`. 

The number of imputations represent the amount of imputed datasets that will be created by mice. Thus with the default `r m` imputations, there are 5 datasets created with imputed data which differ in what values are imputed as a result of random variation. The random variation also has to do with the uncertainty about what value to impute[van Buuren, 2018](https://stefvanbuuren.name/fimd/sec-nutshell.html#fig:miflow). In comparison to a single imputation method like 'mean imputation, the multiple imputation method (obviously) improves the imputation variability. 
Using a greater amount than just 1 imputation, will result in more accurate standard errors, unbiased estimates and better confidence intervals [van Buuren, 2018](https://stefvanbuuren.name/fimd/sec-howmany.html).

The number of iterations, which by default is 5, represent the amount `mice` will iterate over the variables in each imputation. After imputation, convergence should be met for each variable. If not, one could try to enlarge the amount of iterations.

The default methods that `mice` uses to impute the missing values are: `r methS` for smoke, `rmethA` for active, `r methH` for height, `r methW` for weight and `r methB` for bmi. Obviously there are no methods for *age, sex, intensity and rest* since they have no missing values. The `r methS` for smoke uses uses the Bayesian logistic regression method to impute missing data. The `r methA` for active, height, weight and bmi uses the predicitve mean matching method to impute missing data. This "pmm" method starts by defining a linear regression model. 


Table \@ref(tab:predImp) gives an overview of the predictor matrix for the imputations. The 1's represent the column variables that will be used as a predictor to impute the row variable. Logically, the zero's will not be used as predictors for imputations. For example, for *bmi* all variables except bmi are used as predictors to impute bmi. 


