---
title: "Assingment A: Investigating the scope of the missingness problem"
author: "William Schaafsma"
date: "24-2-2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries
```{r libraries, warning = FALSE, message = FALSE}
library(mice)
library(tidyverse)
library(ggplot2)
library(mice)
library(dplyr)
library(naniar)
library(magrittr)

```

## Introduction
For this a assignment we are building a multiple regression model where resting heart rate is the outcome variable. 

The matter of interest will be the impact that incomplete data has on our inferences compared to the inferences we make with complete data.

Therefore our research question states: what impact do missing values have on a "resting heart rate" model inference?

## 2. Loading both observed and true dataset
```{r}
data0 <- readRDS("incomplete_data_g1.rds")
data1 <- readRDS("complete_data.rds")
```

## Quick inspection of both datasets
```{r}
str(data1)
```
*Needs commenting*
```{r}
str(data0)
```
*Needs commenting*
```{r}
summary(data1)
```
*Needs commenting*
```{r}
summary(data0)
```
*Needs commenting*

## Correlation matrix for true database
First select the numeric variables for a quick investigation
*install Hmisc package*
```{r}
num_variables <- dplyr::select_if(data1, is.numeric)
cor_num <- cor(num_variables)
cor_num
```


## Including Plots
```{r pressure, echo=FALSE}

```

## Inspecting missingness
```{r}
md.pattern(data0)
```
In total, the observed dataset contains 540 missing values. The variables **age**, **sex**, **intensity** and **rest** have zero missings. 
```{r}
vis_miss(data0)
```

```{r}
mactive <- is.na(data0$active)#create variable that contains missings
t.test(bmi ~ mactive, data = data1) #testing differences for missings
```
